The Nickname Problem

### 2012-02-24 Nickname problem/src/nickname.tex
Stuffstuffstuff

\begin{dfn}
For a given index of the computable functions $\{\phi_i\}$ we define $i^* = \min\left\{\phi_j : \phi_j \simeq \phi_i\right\}$. That is, the minimal index of a function that is equivalent to $\phi_i$
\end{dfn}

\begin{dfn}
An index of the computable functions $\{\phi_i\}$ is called \textbf{compact} if for every 
$\phi_i(\bar{x}y)$ we have a $\phi_j$ such that $\phi_i(\bar{x}y) \simeq \phi_j(y)$ and  $|j| - |i| \leq |x| + O(1)$
\end{dfn}

@@

A \textbf{non-compact} index would imply a computational metaphor which does not allow this type of manipulation.

\begin{lma}
Let $\{\phi_i\}$ and $\{\psi_j\}$ be two compact, computable enumerations of the computable functions. For a given computable function $\phi_i \simeq \psi_j$,  we have $\mbox{abs}(i^* - j^*) \leq O(1)$ 
\end{lma}
\begin{proof}
Let $\phi_u$ be a universal function for $\psi$, such that $\phi_u(\bar{\imath}x) \simeq \psi_i(x)$. Since $\psi$ is computable this function exists in $\phi$. We have $\psi_{j^*}(x) \simeq \phi_u(\overline{\jmath^*}x)$. By the compactness of $\phi$, we have some $h$ with $|h| \leq |u| + |\overline{\jmath^*}| + O(1)$ such that $\phi_{h}(x) \simeq \phi_u(\overline{\jmath^*}x) \simeq \psi_{j^*}(x)$.

\end{proof}

>>>>

\begin{dfn}
For a given index of the computable functions $\{\phi_i\}$ we define $i^*_\phi = \min\left\{\phi_j : \phi_j \simeq \phi_i\right\}$. That is, the minimal index of a function that is equivalent to $\phi_i$. The subscript may be dropped when it is clear from context.
\end{dfn}

\begin{dfn}
An index of the computable functions $\{\phi_i\}$ is called \textbf{compact} if for every 
$\phi_i(\bar{x}y)$ we have a $\phi_j$ such that $\phi_i(\bar{x}y) \simeq \phi_j(y)$ and  $|j| - |i| \leq |\bar{x}| + O(1)$
\end{dfn}

@@

We can construct a non-compact enumeration by starting with a compact one, and inserting after function $i$ a series of $f(i)$ copies of $\phi_0$, where $f(i)$ is some fast growing function like $2^{i!}$.

\begin{lma}
Let $\{\phi_i\}$ and $\{\psi_j\}$ be two compact, computable enumerations of the computable functions. For a given computable function $\phi_i \simeq \psi_j$,  we have $\mbox{abs}(|i^*| - |j^*|) \leq c(\max(i^*, j^*)) + O(1)$. Where $c(x) \leq 2 \log(|x|) + 1$ is the overhead of prefix encoding $x$
\end{lma}
\begin{proof}
Let $\phi_u$ be a universal function for $\psi$, such that $\phi_u(\bar{\imath}x) \simeq \psi_i(x)$. Since $\psi$ is computable this function exists in $\phi$. We have $\psi_{j^*}(x) \simeq \phi_u(\overline{\jmath^*}x)$. By the compactness of $\phi$, we have some $h$ with $|h| \leq |u| + |\overline{\jmath^*}| + O(1)$ such that $\phi_{h}(x) \simeq \phi_u(\overline{\jmath^*}x) \simeq \psi_{j^*}(x)$.

Thus $|i^*| \leq |h| = |u| + |\overline{\jmath^*}| + O(1) = |j*| + c(\jmath^*) + O(1)$. Reversing $\phi$ and $\psi$ gives us $|j^*| \leq |i^*| + c(i^*) + O(1)$. Combining these, we get the desired result.
\end{proof}

This lemma tells us that so long as we restrict our numberings to be compact and computable, we can never gain more than a logarithmic difference between model sizes. In the limit as $i \rightarrow \infty$, this term represents a vanishing proportion.
